\chapter*{\begin{center}
    ABSTRACT
\end{center}}
 
\quad This document constitutes the summary of the work carried out as part of my end-of-year internship at REDAL in the field of Smart Cities. My mission was to develop an interface between REDAL's internal systems and the DocuSign solution to integrate electronic signatures into the Direct Purchase Request (DAD) process.

\quad This project was managed using the agile approach, which allowed us to be highly responsive to the many changing parameters in our tasks. Thanks to this methodology, we were able to perform quick iterations and receive frequent feedback, thereby improving the quality and relevance of our solution.

\quad The development involved the use of modern technologies such as Node.js for the backend, React.js for the frontend, and the DocuSign API for managing electronic signatures. Setting up a PostgreSQL database was also necessary to store and manage the data of documents and signatories.

\quad In addition to the technical aspect, this project allowed me to develop skills in project management and teamwork, while deepening my knowledge of security and the management of sensitive data.

\quad In conclusion, this internship was an enriching and formative experience, enabling me to contribute to an innovative project and develop valuable technical and professional skills.



\vspace{0.5cm}


\noindent\rule[2pt]{\textwidth}{0.5pt}

{\textbf{Keywords :}}
DocuSign,
Smart Cities,
Electronic Signatures,
Direct Purchase Requests (DPR),
DocuSign API,
Web Development,
Process Automation,

\noindent\rule[2pt]{\textwidth}{0.5pt}







